---
title: "HW4_report"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 107023058

## Question 1
Description: Google compute a DOI score for each app to determine whether they are maleware. DOI score is binomially distrbuted.

### (a)
Given the critical DOI score(-3.7), find the probability that a randomly chosen app from Google’s app store will turn off the Verify security feature.

```{r}
pnorm(-3.7) # those apps whose Z-score are lower than -3.7 have lower retention rate
```

### (b)
Assuming there were 2.2 million apps, what number of apps on the Play Store did Google expect would maliciously turn off the Verify feature once installed
```{r}
num_app <- 2.2*10^6
low_retention <- num_app * pnorm(-3.7)
low_retention
```

## Question 2
Description: Verizon claims that they take 7.6 minutes to repair phone services for its customers on average.

### (a) The Null distribution of t-values

(i) Visualize the distribution of Verizon’s repair times, marking the mean with a vertical line
```{r}
RepairTime <- read.csv("D:/Retro/NTHU/課程講義/大三/計算統計於商業分析之應用/HW4/verizon.csv",header = TRUE)
repair_time <- RepairTime$Time
plot(density(repair_time),main = 'Distribution of Repair Time') 
abline(v = mean(repair_time),col = 'red')
```

(ii) Given what PUC wishes to test, how would you write the hypothesis?
   h0: u = 7.6  h1:u!=7.6  with a = 0.01

(iii) Estimate the population mean, and the 99% confidence interval (CI) of this estimate
```{r}
mean_hypo <- 7.6  # set null mean as 7.6
mean_repair_time <- mean(repair_time)
sd_repair_time <- sd(repair_time)
ci99 <- c(mean_repair_time-2.58*(sd_repair_time/sqrt(length(repair_time))),mean_repair_time+2.58*(sd_repair_time/sqrt(length(repair_time))))
# compute its 99% C.I
ci99
```

(iv) find the t-statistic and p-value of the test
```{r}
se <- sd(repair_time)/sqrt(length(repair_time)) # compute standard error
t_value <- (mean_repair_time-mean_hypo)/se # compute t-value
df<- length(repair_time)-1 # degree of freedom
p_value <- 1- pt(t_value,df) # compute p-value
t_value;p_value

qt(0.995,df) # the critical point of t-test 
```

(v) Briefly describe how these values relate to the Null distribution of t (not graded)
- ANS:

(vi) What is your conclusion about the advertising claim from this t-statistic, and why?
- ANS: 

### (b) bootstrapping on the sample data to examine this problem

(i) Bootstrapped Percentile: Estimate the bootstrapped 99% CI of the mean
```{r}
compute_sample_mean <- function(sample0) {
  resample <- sample(sample0, length(sample0), replace=TRUE)
  mean(resample)
}
boostrap_mean<- replicate(2000,compute_sample_mean(repair_time)) # bootstrapping

boostrap_ci99 <- quantile(boostrap_mean,probs = c(0.005,0.995)) # take 0.005% and 0.995% quantile as 99% CI
boostrap_ci99
```

(ii) What is the 99% CI of the bootstrapped difference between the population mean and the hypothesized mean?
```{r}
boot_mean_diffs <- function(sample0, mean_hyp) {
  resample <- sample(sample0, length(sample0), replace=TRUE)
  return( mean(resample) - mean_hyp )
}
mean_diffs <- replicate(2000,boot_mean_diffs(repair_time,mean_hypo)) # bootstrapping
diff_ci_99 <- quantile(mean_diffs,probs = c(0.005,0.995)) # take 0.005% and 0.995% quantile as 99% CI
diff_ci_99
```

(iii) What is 99% CI of the bootstrapped t-statistic?
```{r}
boot_t_stat <- function(sample0, mean_hyp) {
  resample <- sample(sample0, length(sample0), replace=TRUE)
  diff <- mean(resample) - mean_hyp
  se <- sd(resample)/sqrt(length(resample))
  return( diff / se )
}
t_boots <- replicate(2000, boot_t_stat(repair_time, mean_hypo)) # bootstrapping
t_stat_ci99 <- quantile(t_boots,probs= c(0.005,0.995)) # take 0.005% and 0.995% quantile as 99% CI
t_stat_ci99
```

(iv) Plot separate distributions of all three bootstraps above
```{r}
plot(density(t_boots))
abline(v = mean(t_boots),col = 'red')

plot(density(mean_diffs))
abline(v = mean(mean_diffs),col = 'red')

plot(density(boostrap_mean))
abline(v = mean(boostrap_mean),col = 'red')
```

### (c)
Do the four methods (traditional test, bootstrapped percentile, bootstrapped difference of means, bootstrapped t-Interval) agree with each other on the test?